\documentclass[a4paper, 12pt, answers]{exam}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{bm}
\usepackage{advdate}
\usepackage{datetime}
\usepackage[mathcal]{eucal}
\usepackage{dsfont}
\usepackage[numbered,framed]{matlab-prettifier}
\usepackage{tkz-euclide}
\usetkzobj{all}
\usepackage{url}
\newdate{issuedate}{27}{9}{2019}
\newdate{duedate}{11}{10}{2019}

% \newcommand{\duedate}[1][14]{%
% \begingroup
% \AdvanceDate[#1]%
% \today%
% \endgroup
% }%

\input{lddef}

\makeatletter
\@ifclasswith{exam}{answers}{\newcommand{\firstblock}{comments_ldps1}}{\newcommand{\firstblock}{policies}}
\makeatother

\begin{document}

\pagestyle{headandfoot}
\runningheadrule


\newcounter{psctr}
\setcounter{psctr}{1} % set to the times of problem

\runningheader{Programming Assignment \thepsctr}
              {\textsc{Learning from Data}}
              { Page \thepage\ of \numpages}
\firstpagefooter{}{}{}
\runningfooter{}{}{}


\newcounter{Sequ}
\newenvironment{Sequation}
   {\stepcounter{Sequ}%
     \addtocounter{equation}{-1}%
     \renewcommand\theequation{S\arabic{Sequ}}\equation}
   {\endequation}
%\topskip0pt

% \vspace*{\fill}
\centering

% \vspace{0.3em}
\centering
\renewcommand{\thequestion}{\arabic{psctr}.\arabic{question}}
\courseheader

\begin{center}
  \underline{\bf Programming Assignment \thepsctr} \\
\end{center}
\begin{flushleft}
  \textbf{Issued:} \displaydate{issuedate} \hfill
  \textbf{Due:} \displaydate{duedate} 
\end{flushleft}

\hrule 

\input{\firstblock}

%\pointname{}
%\vspace{\footskip}
\vspace{1em}


%\pointname{}
%\vspace{\footskip}
%\vspace{1em}

\begin{questions}
\question (5 points) \emph{Linear regression.} Consider the linear observation model
\begin{equation*}
\by = X\bw + \bc
\end{equation*}
where the $X$ is a $10000 \times 10$ matrix, and $\bw,\bc$ are column vectors with length 10 and 10000. Use gradient descent to find the $a$ that minimizes the loss $\frac12 \|X\bw-y\|^2_2$. See details in the \textbf{linear\_regression.py}.



\question (5 points) \emph{Logistic regression.} The MNIST database contains 60000 training images and 10000 testing images. In this task, each image of the MNIST has been reshaped to a column vector of length $28\times28=784$. You need to calculate the gradient and update the weights to learn your model. See details in the \textbf{logistic\_regression.py}.

\end{questions}


\nocite{*}
\begin{flushleft}
\textbf{Notice}: \\
\begin{enumerate}
\item Use matrix operations other than loops for efficiency. If the running time exceeds 5 minutes, you will get point deductions.
\item You are ought to acquire at leat $95\%$ test accuracy in your logistic binary classifier. 
\end{enumerate}
\end{flushleft}

\bibliographystyle{plain}
\bibliography{ref}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

%  LocalWords:  headandfoot covariance
